---
title: "renewal_analysis"
author: "Sarah Deussing"
date: "2025-04-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data
```{r}
library(readxl)
account_status <- read.csv('reds_wheelhouse_edw_nd_account_status.csv')
buyer_types <- read_excel('reds_wheelhouse_edw_nd_buyer_types.xlsx')
demographics <- read.csv('reds_wheelhouse_edw_nd_demographics.csv')
promotions <- read.csv('reds_wheelhouse_edw_nd_promotions.csv')
ticket_sales <- read.csv('reds_wheelhouse_edw_nd_ticket_sales_3.csv')
```

## Find tenured customers
```{r}
library(dplyr)
tenure <- account_status %>% group_by(ACCOUNT_KEY) %>% 
  filter(max(TENURE) > 1) %>% 
  arrange(ACCOUNT_KEY, SEASON_YEAR, FIRST_PURCHASE_DATE) %>%
  select(ACCOUNT_KEY, SEASON_YEAR) %>% distinct()

tenure <- merge(tenure, ticket_sales[, c("ACCOUNT_KEY", "SEASON_YEAR", "BUYER_TYPE_CODE")], 
                by = c("ACCOUNT_KEY", "SEASON_YEAR"), all.x = TRUE)

tenure <- tenure %>%
  group_by(ACCOUNT_KEY, SEASON_YEAR) %>%
  summarise(BUYER_TYPE_CODE = paste(unique(BUYER_TYPE_CODE), collapse = ", "), .groups = 'drop')

tenure2 <- tenure %>% filter(BUYER_TYPE_CODE != "NA")
tenure2$TENURE <- tenure2$RENEWED <- tenure2$KEPT_CODES <- tenure2$UNKEPT_CODES <- NA
```

## Count Changes to Purchases by Year (Renew Behavior)
```{r}
renew_behavior <- data.frame(ACCOUNT_KEY = character(),
                             SEASON_YEAR = numeric(),
                             BUYER_TYPE_CODE = character(),
                             TENURE = numeric(),
                             RENEWED = numeric(),
                             KEPT_CODES = character(),
                             UNKEPT_CODES = character())

accounts <- unique(tenure2$ACCOUNT_KEY)

for (a in accounts) {
    temp <- tenure2[tenure2$ACCOUNT_KEY == a, ]
    temp <- temp[order(temp$SEASON_YEAR), ]
    
    years <- unique(temp$SEASON_YEAR)
    all_years <- seq(from = min(temp$SEASON_YEAR), to = max(temp$SEASON_YEAR), by = 1)
    missing <- setdiff(all_years, years)
    if (length(missing) > 0) {
      df <- data.frame(ACCOUNT_KEY = rep(a, length(missing)), SEASON_YEAR = missing,
                       BUYER_TYPE_CODE = rep(NA, length(missing)), TENURE = rep(NA, length(missing)), 
                       RENEWED = rep(NA, length(missing)), 
                       KEPT_CODES = rep(NA, length(missing)), UNKEPT_CODES = rep(NA, length(missing)))
      temp <- rbind(temp, df)
      temp <- temp[order(temp$SEASON_YEAR), ]
    }
  
    # new columns
    renewed <- rep(0, nrow(temp))
    tenured <- rep(1, nrow(temp))
    kept_codes <- unkept_codes <- rep(NA, nrow(temp))
    renew_val <- 0
    tenure_val <- 1
    for (i in 1: nrow(temp)) {
      if (i == 1) {renew_val <- 0 
                  tenure_val <- 1}
      else {
        
        # if they purchased something that year (buyer code is not NA)
        if (!is.na(temp$BUYER_TYPE_CODE[i])) { 
          tenure_val <- tenure_val + 1 # increment tenure val
          
          curr_codes <- unlist(strsplit(temp$BUYER_TYPE_CODE[i], ", "))
          prev_codes <- unlist(strsplit(temp$BUYER_TYPE_CODE[i-1], ", "))
        
          kept_codes[i] <- paste(intersect(curr_codes, prev_codes), collapse = ", ")
          unkept_codes[i] <- paste(setdiff(curr_codes, prev_codes), collapse = ", ")
        
          # increment renew val
          if (length(intersect(curr_codes, prev_codes) > 0)) { renew_val <- renew_val + 1 }
          else { renew_val <-  0 }
        }
        
        # they did not purchase anything
        else {tenure_val <- 1 
              renew_val <- 0
              kept_codes[i] <- "none"
              unkept_codes[i] <- "none"}
      }
      
      renewed[i] <- renew_val
      tenured[i] <- tenure_val
    }
    temp$RENEWED <- renewed
    temp$TENURE <- tenured
    temp$KEPT_CODES <- kept_codes
    temp$UNKEPT_CODES <- unkept_codes
    
    renew_behavior <- rbind(renew_behavior, 
                            temp[, c("ACCOUNT_KEY", "SEASON_YEAR", "BUYER_TYPE_CODE", "TENURE", "RENEWED", 
                                     "KEPT_CODES", "UNKEPT_CODES")])
}
```

Stats
```{r}
# most common kept code
kept_codes_table <- table(renew_behavior$KEPT_CODES[!renew_behavior$KEPT_CODES %in% c("", "none")])
names(kept_codes_table)[which.max(kept_codes_table)]

# most common unkept code
unkept_codes_table <- table(renew_behavior$UNKEPT_CODES[!renew_behavior$UNKEPT_CODES %in% c("", "none")])
names(unkept_codes_table)[which.max(unkept_codes_table)]
```

```{r}
# longest tenure
renew_behavior[which.max(renew_behavior$TENURE), c("ACCOUNT_KEY", "TENURE")]

# longest renew
renew_behavior[which.max(renew_behavior$RENEWED), c("ACCOUNT_KEY", "RENEWED", "KEPT_CODES")]
```

Demographics of Renewing/Moving
```{r}
library(tidyr)
renew_behavior_demo <- renew_behavior %>%
  left_join(demographics, by = "ACCOUNT_KEY")

renew_behavior_demo <- renew_behavior_demo %>%
  mutate(AGE_GROUP = cut(AGE, breaks = c(17, 25, 35, 45, 55, 65, Inf),
                    labels = c("18–25", "26–35", "36–45", "46–55", "56–65", "66+")))


top10_age <- renew_behavior_demo %>%
  filter(!is.na(BUYER_TYPE_CODE) & !is.na(AGE_GROUP)) %>%
  group_by(AGE_GROUP, BUYER_TYPE_CODE) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  arrange(AGE_GROUP, desc(Count)) %>%
  group_by(AGE_GROUP) %>%
  slice_head(n = 10)

location_behavior <- renew_behavior %>%
  left_join(ticket_sales %>% select(ACCOUNT_KEY, SEASON_YEAR, CITY, STATE),
            by = c("ACCOUNT_KEY", "SEASON_YEAR"))
location_behavior <- location_behavior %>%
  separate_rows(BUYER_TYPE_CODE, sep = ",\\s*") %>%
  filter(!is.na(BUYER_TYPE_CODE) & !is.na(CITY) & !is.na(STATE)) %>%
  group_by(CITY, STATE, BUYER_TYPE_CODE) %>%
  summarise(Count = n(), .groups = 'drop')
```

Non-renewals
```{r}

```


## Ticket Use %
```{r}
# overall
ticket_use_perc <- sum(ticket_sales$SCAN_COUNT, na.rm = TRUE) / nrow(ticket_sales)
ticket_use_perc

# by year
ticket_use_yearly <- ticket_sales %>%
  select(SEASON_YEAR, SCAN_COUNT) %>%
  group_by(SEASON_YEAR) %>%
  summarize(perc_use = sum(SCAN_COUNT, na.rm = TRUE) / n())
ticket_use_yearly

# by game
ticket_use_by_game <- ticket_sales %>%
  select(EVENT_NAME, SCAN_COUNT) %>%
  group_by(EVENT_NAME) %>%
  summarize(perc_use = sum(SCAN_COUNT, na.rm = TRUE) / n()) %>% arrange(desc(perc_use))
ticket_use_by_game

# by buyer type code
ticket_use_by_code <- ticket_sales %>%
  select(BUYER_TYPE_CODE, SCAN_COUNT) %>%
  group_by(BUYER_TYPE_CODE) %>%
  summarize(perc_use = sum(SCAN_COUNT, na.rm = TRUE) / n(),
            total_count = n()) %>% arrange(desc(total_count))
ticket_use_by_code
```

```{r}
renew_behavior_return_after_gap <- data.frame(
  ACCOUNT_KEY = character(),
  SEASON_YEAR = numeric(),
  BUYER_TYPE_CODE = character(),
  TENURE = numeric(),
  RENEWED = numeric(),
  KEPT_CODES = character(),
  UNKEPT_CODES = character(),
  RETURNED_AFTER_GAP = numeric(),
  stringsAsFactors = FALSE
)

accounts <- unique(tenure2$ACCOUNT_KEY)

for (a in accounts) {
  # Only keep necessary columns
  temp <- tenure2[tenure2$ACCOUNT_KEY == a, c("ACCOUNT_KEY", "SEASON_YEAR", "BUYER_TYPE_CODE")]
  temp <- temp[order(temp$SEASON_YEAR), ]
  
  years <- temp$SEASON_YEAR
  all_years <- seq(min(years), max(years))
  missing <- setdiff(all_years, years)
  
  if (length(missing) > 0) {
    fill <- data.frame(
      ACCOUNT_KEY = rep(a, length(missing)),
      SEASON_YEAR = missing,
      BUYER_TYPE_CODE = rep(NA, length(missing)),
      stringsAsFactors = FALSE
    )
    temp <- rbind(temp, fill)
    temp <- temp[order(temp$SEASON_YEAR), ]
  }
  
  # Add all required columns upfront
  temp$TENURE <- NA
  temp$RENEWED <- NA
  temp$KEPT_CODES <- NA
  temp$UNKEPT_CODES <- NA
  temp$RETURNED_AFTER_GAP <- NA
  
  renewed <- rep(0, nrow(temp))
  tenured <- rep(1, nrow(temp))
  kept_codes <- unkept_codes <- rep(NA, nrow(temp))
  returned_after_gap <- rep(0, nrow(temp))
  renew_val <- 0
  tenure_val <- 1
  
  for (i in 1:nrow(temp)) {
    if (i == 1) {
      renew_val <- 0
      tenure_val <- 1
    } else {
      if (!is.na(temp$BUYER_TYPE_CODE[i])) {
        tenure_val <- tenure_val + 1
        
        curr_codes <- unlist(strsplit(temp$BUYER_TYPE_CODE[i], ", "))
        prev_codes <- unlist(strsplit(temp$BUYER_TYPE_CODE[i - 1], ", "))
        
        kept_codes[i] <- paste(intersect(curr_codes, prev_codes), collapse = ", ")
        unkept_codes[i] <- paste(setdiff(curr_codes, prev_codes), collapse = ", ")
        
        if (length(intersect(curr_codes, prev_codes)) > 0) {
          renew_val <- renew_val + 1
        } else {
          renew_val <- 0
        }
      } else {
        tenure_val <- 1
        renew_val <- 0
        kept_codes[i] <- "none"
        unkept_codes[i] <- "none"
      }
    }
    
    renewed[i] <- renew_val
    tenured[i] <- tenure_val
  }
  
  
  for (i in 2:nrow(temp)) {
    if (!is.na(temp$BUYER_TYPE_CODE[i])) {
      if (any(is.na(temp$BUYER_TYPE_CODE[max(1, i - 2):(i - 1)]))) {
        returned_after_gap[i] <- 1
      }
    }
  }
  
  temp$RENEWED <- renewed
  temp$TENURE <- tenured
  temp$KEPT_CODES <- kept_codes
  temp$UNKEPT_CODES <- unkept_codes
  temp$RETURNED_AFTER_GAP <- returned_after_gap
  
  renew_behavior_return_after_gap <- rbind(renew_behavior_return_after_gap, temp)
}

```




This has lists churners and last code they purchased

```{r}


latest_season <- max(ticket_sales$SEASON_YEAR, na.rm = TRUE)


account_last_seen <- ticket_sales %>%
  filter(!is.na(BUYER_TYPE_CODE)) %>%
  group_by(ACCOUNT_KEY) %>%
  arrange(SEASON_YEAR) %>%
  summarise(
    Last_Active_Season = last(SEASON_YEAR),
    Last_BUYER_TYPE_CODE = last(BUYER_TYPE_CODE),
    .groups = "drop"
  )

account_last_seen <- account_last_seen %>%
  mutate(Churned = Last_Active_Season < latest_season)

churners <- account_last_seen %>% 
  filter(Churned== "TRUE") %>% 
  mutate(Years_Gone=latest_season-Last_Active_Season)
  

```

Churners with Demographics

```{r}
churners_with_demo <- churners %>%
  left_join(demographics, by = "ACCOUNT_KEY")
```

Churner Demo Breakdown

```{r}

churners_with_demo %>%
  mutate(
    GENDER = ifelse(GENDER == "", "Unknown", GENDER),
    MARITAL_STATUS = ifelse(MARITAL_STATUS == "", "Unknown", MARITAL_STATUS)
  ) %>%
  summarise(
    avg_age = mean(AGE, na.rm = TRUE),
    median_income = median(INCOME_MIDPOINT, na.rm = TRUE),
    gender_dist = paste(names(table(GENDER)), table(GENDER), sep = ": ", collapse = ", "),
    marital_status_dist = paste(names(table(MARITAL_STATUS)), table(MARITAL_STATUS), sep = ": ", collapse = ", "),
    pct_with_children = mean(CHILDREN_IN_HH == "Y", na.rm = TRUE)
  )


```

Age distribution of churners

```{r}
library(ggplot2)

churners_with_demo %>%
  filter(!is.na(AGE)) %>%
  mutate(
    AGE_GROUP = cut(
      AGE,
      breaks = c(17, 25, 35, 45, 55, 65, Inf),
      labels = c("18–25", "26–35", "36–45", "46–55", "56–65", "66+"),
      right = TRUE
    )
  ) %>%
  count(AGE_GROUP) %>%
  ggplot(aes(x = AGE_GROUP, y = n, fill = AGE_GROUP)) +
  geom_bar(stat = "identity") +
  labs(title = "Age Group Distribution of Churners", x = "Age Group", y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")

```
Gender Breakdown of Churners

```{r}
churners_with_demo %>%
  filter(GENDER != "") %>%
  count(GENDER) %>%
  ggplot(aes(x = GENDER, y = n, fill = GENDER)) +
  geom_bar(stat = "identity") +
  labs(title = "Gender Breakdown of Churners", y = "Count", x = "Gender") +
  theme_minimal()
```
Marital Status and Children Status of Churners

```{r}

churners_with_demo %>%
  filter(MARITAL_STATUS != "") %>%
  mutate(
    CHILDREN_IN_HH = case_when(
      CHILDREN_IN_HH == "Y" ~ "Y",
      CHILDREN_IN_HH == "N" ~ "N",
      TRUE ~ "Unknown"
    ),
    CHILDREN_IN_HH = factor(CHILDREN_IN_HH, levels = c("Y", "N", "Unknown"))
  ) %>%
  count(MARITAL_STATUS, CHILDREN_IN_HH) %>%
  ggplot(aes(x = MARITAL_STATUS, y = n, fill = CHILDREN_IN_HH)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Marital Status & Children in Household", y = "Count", fill = "Children in HH") +
  theme_minimal()



```
Top Churn Codes

```{r}
top_churn_codes <- churners %>% 
  count(Last_BUYER_TYPE_CODE) %>%
  arrange(desc(n)) %>% 
  slice_head(n=10)

print(top_churn_codes)
```

Churn Rate Per Year

```{r}
library(purrr)

buyers_per_year <- ticket_sales %>%
  select(ACCOUNT_KEY, SEASON_YEAR) %>%
  distinct()


churn_data_per_year <- buyers_per_year %>%
  group_by(SEASON_YEAR) %>%
  summarise(
    buyers = list(unique(ACCOUNT_KEY)),
    total_buyers = n()
  ) %>%
  arrange(SEASON_YEAR) %>%
  mutate(
    next_year_buyers = lead(buyers),
    retained_buyers = map2_int(buyers, next_year_buyers, ~ sum(.x %in% .y)),
    churned_buyers = total_buyers - retained_buyers,
    churn_rate = churned_buyers / total_buyers
  )

churn_data_cleaned <- churn_data_per_year %>%
  filter(lengths(next_year_buyers) > 0)

churn_data_cleaned %>%
  select(SEASON_YEAR, total_buyers, retained_buyers, churned_buyers, churn_rate)



```

Churn Rate Per Year By Type
```{r}



buyers_by_year_type <- ticket_sales %>%
  select(ACCOUNT_KEY, SEASON_YEAR, BUYER_TYPE_CODE) %>%
  distinct()


buyers_churn_by_type <- buyers_by_year_type %>%
  group_by(SEASON_YEAR, BUYER_TYPE_CODE) %>%
  summarise(
    buyers = list(unique(ACCOUNT_KEY)),
    total_buyers = n(),
    .groups = "drop"
  ) %>%
  arrange(SEASON_YEAR) %>%
  mutate(next_year = SEASON_YEAR + 1) %>%
  left_join(
    buyers_by_year_type %>%
      group_by(SEASON_YEAR) %>%
      summarise(all_buyers_next = list(unique(ACCOUNT_KEY)), .groups = "drop"),
    by = c("next_year" = "SEASON_YEAR")
  ) %>%
  mutate(
    retained = map2_int(buyers, all_buyers_next, ~ sum(.x %in% .y)),
    churned = total_buyers - retained,
    churn_rate = churned / total_buyers
  ) %>%
  select(SEASON_YEAR, BUYER_TYPE_CODE, total_buyers, retained, churned, churn_rate) %>%
  filter(SEASON_YEAR !=2024)  


```



